---
title: "Meu primeiro relatório em Quarto"
subtitle: "Este é um subtítulo"
author: "José de Jesus Filho"
date: "05/06/2023"
toc: true
format: 
    html: default
    pdf: default
    docx: default
editor: visual
execute: 
  echo: false
  warning: false
  message: false
bibliography: biblio.bib
csl: abnt.csl
---

## Quarto

Quarto enables you to **weave** together/ content and executable code into a finished document. To learn more about Quarto see [clique aqui](https://quarto.org)

## Running Code

| Col1 | Col2 | Col3 |
|------|------|------|
| jjd  | ddd  |      |
|      |      |      |
|      |      |      |

When you click the **Render** *button* a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
#| echo: true
#| message: false
#| warning: false
hist(rnorm(1000))
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).


Como diria Zabala [@zabala]


Igualmente, Luvizotto entende que o conceito de jurimetria é polissêmico [@luvizotto]
